Combinatorial interpretations of holonomic recurrences

### 2021-08-16 article/main.tex
Add more images

\RequirePackage[utf8]{inputenc}
\DeclareUnicodeCharacter{00A0}{ }

@@

\RequirePackage{geometry}
\RequirePackage{graphicx}
\RequirePackage{svg}

@@

\begin{center}
    \begin{minipage}[t]{.2\textwidth}
        \begin{center}
            \(B\)\\
            \includesvg[scale=0.5]{binary_tree_def_1}%
        \end{center}
    \end{minipage}%
    \begin{minipage}[t]{.05\textwidth}
        \begin{center}
            \(=\)\\
        \end{center}
    \end{minipage}%
    \begin{minipage}[t]{.2\textwidth}
        \begin{center}
            \(\text{leaf}\)\\
            \includesvg[scale=0.5]{binary_tree_def_2}%
        \end{center}
    \end{minipage}%
    \begin{minipage}[t]{.05\textwidth}
        \begin{center}
            \(+\)\\
        \end{center}
    \end{minipage}%
    \begin{minipage}[t]{.2\textwidth}
        \begin{center}
            \(B^2\)\\
            \includesvg[scale=0.5]{binary_tree_def_3}%
        \end{center}
    \end{minipage}%
\end{center}

@@

\begin{example}
    \(\n \n \no \n \no \no \no\)
    \begin{center}
        \includesvg[scale=.7]{oononnn}
    \end{center}
\end{example}

We also can define prefix and suffix of \(T\).

@@

\todo{Add some illustration}

@@

\todo{image of transformation unary-binary to full-binary}

@@

To present the interpretation in bijective language, we will have to introduce several types of the the virtual leaves (you may want to revisit section \ref{sub:notation} Notation):

\begin{enumerate}
    \item Vro - virtual leaf being right virtual-oneling;
    \item Vrt - virtual leaf being right virtual-twinling. We will divide this case into:
        \begin{enumerate}
            \item VrtUrv - Vri which uncle is a right virtual leaf;
            \item VrtUra - Vri which uncle is a right actual node;
            \item VrtUla - Vri which uncle is a left actual node.
        \end{enumerate}
    \item Vlt - virtual leaf left virtual-twinling. Note that from definition \ref{def:unary_binary_2}, left virtual leave can not have sibling being a actual node. We can divide also this case into:
        \begin{enumerate}
            \item VltUrv - Vlt which uncle is a right virtual leaf;
            \item VltUra - Vlt which uncle is a right actual node;
            \item VltUla - Vlt which uncle is a left actual node.
        \end{enumerate}
\end{enumerate}

@@

\todo{draw the transformations}

@@

\todo{example}

>>>>

\RequirePackage[utf8]{inputenc}
\DeclareUnicodeCharacter{00A0}{ }
\DeclareUnicodeCharacter{25CF}{\(\n\)}

@@

\RequirePackage{geometry}
\RequirePackage{tabularx}
\RequirePackage{graphicx}
\RequirePackage{svg}

@@

\begin{figure}[h]
    \begin{center}
        \begin{minipage}[t]{.2\textwidth}
            \begin{center}
                \(B\)\\
                \includesvg[scale=0.5]{binary_tree_def_1}%
            \end{center}
        \end{minipage}%
        \begin{minipage}[t]{.05\textwidth}
            \begin{center}
                \(=\)\\
            \end{center}
        \end{minipage}%
        \begin{minipage}[t]{.2\textwidth}
            \begin{center}
                \(\text{leaf}\)\\
                \includesvg[scale=0.5]{binary_tree_def_2}%
            \end{center}
        \end{minipage}%
        \begin{minipage}[t]{.05\textwidth}
            \begin{center}
                \(+\)\\
            \end{center}
        \end{minipage}%
        \begin{minipage}[t]{.2\textwidth}
            \begin{center}
                \(B^2\)\\
                \includesvg[scale=0.5]{binary_tree_def_3}%
            \end{center}
        \end{minipage}%
    \end{center}
    \caption{Binary tree recursive definition}
    \label{fig:binary_recursion}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includesvg[scale=.7]{oononnn}
    \caption{\(\n \n \no \n \no \no \no\)}
    \label{fig:oononnn}
\end{figure}

We can also define prefix and suffix of \(T\).

@@

\begin{figure}[h]
    \centering
    \begin{minipage}{.25\textwidth}\includesvg[scale=0.35]{remy_base}\end{minipage}%
    \(\Rightarrow\)
    \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{remy_left}\end{minipage}%
    \caption{\(\enc{R_l(T, v)}\)}
    \label{fig:remy_left}
\end{figure}

\begin{figure}[h]
    \centering
    \begin{minipage}{.25\textwidth}\includesvg[scale=0.35]{remy_base}\end{minipage}%
    \(\Rightarrow\)
    \begin{minipage}{.4\textwidth}\includesvg[scale=0.5]{remy_right}\end{minipage}%
    \caption{\(\enc{R_r(T, v)}\)}
    \label{fig:remy_right}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includeinlinesvg{.2}{unary_binary_base}%
    \(\Rightarrow\)%
    \includeinlinesvg{.3}{unary_binary_full}
    \caption{Unary-binary tree to full-binary tree transformation}
    \label{fig:unary_binary_transformation}
\end{figure}

@@

To present the interpretation in bijective language, we will have to introduce several types of the the nodes (you may want to revisit section \ref{sub:notation} Notation):

\begin{enumerate}
    \item Vro - virtual leaf being right virtual-oneling;
    \item Vrt - virtual leaf being right virtual-twinling. We will divide this case into:
        \begin{enumerate}
            \item VrtUrv - Vri which uncle is a right virtual leaf;
            \item VrtUra - Vri which uncle is a right actual node;
            \item VrtUla - Vri which uncle is a left actual node.
        \end{enumerate}
    \item Vlt - virtual leaf left virtual-twinling. Note that from definition \ref{def:unary_binary_2}, left virtual leave can not have sibling being a actual node. We can divide also this case into:
        \begin{enumerate}
            \item VltUrv - Vlt which uncle is a right virtual leaf;
            \item VltUra - Vlt which uncle is a right actual node;
            \item VltUla - Vlt which uncle is a left actual node;
        \end{enumerate}
    \item I - Internal node.
\end{enumerate}

@@

\begin{center}
    \begin{tabular}{| c | c | c |}
        \hline

        \(U(n-2)\) &
        \(U(n-1)\) &
        \(U(n)\)\\
        \hline

        &
        I \includesvg[scale=0.4]{ub_1si} &
        Vro \includesvg[scale=0.4]{ub_0fid} \\
        \hline
    \end{tabular}
\end{center}
\todo{finish the table}

@@

\begin{figure}[h]
    \centering
    \includesvg[scale=0.4]{schroder_1}
    \includesvg[scale=0.4]{schroder_2}
    \includesvg[scale=0.4]{schroder_3}
    \includesvg[scale=0.4]{schroder_4}
    \(\ldots\)
    \caption{Schröder tree node}
    \label{fig:schroder_trees}
\end{figure}
